Numerical simulation of bubble deformation \\ and breakup under simple linear shear flows

### 2024-11-29 Revised-paper/Reply/Reply-Reviewer1.tex

Please find enclosed the revised version of our manuscript (CES-D-24-01867):
``Numerical Simulation of Bubble Deformation and Breakup under 
Simple Linear Shear Flows''.
We thank the reviewers for their comments and thoughts regarding improvement 
of our paper. We believe that we have addressed all of the reviewers’ 
concerns; the changes are itemized in detail below.

\par\noindent
NOTE: all references to equations and figures below are with
reference to the numbering scheme of the revised version of the paper,
not the original version.  Also, changes are hi-lighted in red.
\par\noindent

Changes made in response to comments of Reviewer 1: \begin{enumerate}
%%1
\item
\textsf
{Abstract, hightlights, and introduction are written in a way that confuses the reader: the text jumps back and forth between bubbles and drops as well as shear flows and other flow configurations. Then it suddenly moves to lift and deformation rather than breakup. Finally a number of random applications are mentioned without any relation to bubble breakup. The authors should clearly state what their contrbution is from the outset. The reader will not go on until the end to figure that out by himself. The use of shorter paragraphs each addressing a single issue is very helpful.}
\vspace{3 mm}

Response: \\
We have gone through the whole paper fixing the grammar and the organization.  We believe the message is very clear now. \\
\\

@@

%%2
\item
\textsf
{Method: The use of only 2 levels of grid refinement appears odd. For an accurate representation of the flow near the interface a very fine mesh is typically needed. Only 32 cells over the bubble diameter is hardly sufficient ot get accurate results as corroborated by the mediorce agreement of the presented simulation results with the experimental data used for validation. Two more levels of grid refinement are likely needed to resolved the flow near the bubble while farther away some coarsening may be possible. Optimizing the grid is imperative in a situaltion like the considerd one due to the strong deformation of the bubble which high curvature of the interface and the singular nature of the breakup event. Fully capturing the breakup, which represents a topological singularity, is impossible without a subgrid scale model.}
\vspace{3 mm}

Response: \\
We disagree with the referee here.  The resolution used for our results is enough.  The results shown in Figure 3 are very convincing in that if we refined the grid more, the results would hardly change.  In addition, we have the results in Tables I and II which compare our results to other researchers' simulations and experiments for bubble/drop deformation in shear flows. Finally, at the top of section 3.2, we now list a number of references involving bubbles and drops with severe deformation in which our method was validated by way of grid refinement studies and comparison with experiments.

There is a large hole in the research in which our results fit in: this is the low Capillary number, Moderate to High Reynolds number regime.  In this void, it is impossible to do experiments unless one is in a microgravity environment.  At the same time, numerical algorithms must be designed in order to robustly and accurately predict the tensile strength of a bubble in the low capillary, moderate to high Reynolds number regime, in which ours is the first.  We believe that the results as currently presented, fill the void and that they should be reported now rather than waiting another year.

@@

Perhaps in future work, in which we have more computing power available to us, we can try an extra refinement, albeit, the results are most likely a foregone conclusion in that they will be in close agreement with the results that we already have.  Also as future work, it is inevitable that researchers will be able to run experiments on the space station which corroborate the results of our simulations that we have now.

We have added ``Remark 1'' and ``Remark 2'' in section 3.1 which makes it clear why adding another level of refinement would delay the publication of our work by another four years, and why sub-scale models are unnnecessary at pinch off for the bubble deformation under simple shear flow problem.  Again, the results that we have now are publishable and will make an impact, it would be fruitless to wait another 4 years.

@@

%%3
\par\noindent
\item
\textsf
{Results: Mostly just pictures are shown from which little is to be learned. The only results of which future use can be expected is the regime map in Fig. 12. Bu this is also only qualitative and based on very few data points. More combinations of Ca and Re should be provided and a quantitative fit to the regime boundary be obtained. Moreover only two values of density and viscosity ratio equal to 1 and ~0.001 are used. An investigation of intermediate values would be straight forward and would allow to provide also models for the influence of these obviously important parameters. In particular it should be clarified whether the difference in behavior is more due to the density ration or more due to the viscosity ratio. Also it needs to be investigated how small these ratios need to be for the gas phase properties to be considered as negligibly small. For the practically important case of air bubbles in water the viscosity ratio is 0.02, an order of magnitude larger than considered in the paper. Whether this can already be considered negligible or not remains unclear.}
\vspace{3 mm}

Response: \\
We have added more snapshots to Figure 4, plotted the velocity field in Figure 9,  and added appropriate accompanying analysis to the text (in response to reviewer 2), but otherwise, we disagree with this comment.  We already report many novel and significant results and sufficiently analyze the data both with strategic plots and quantitative tables.  Adding more results would only needlessly delay the paper another year.  
\par
We do agree with the referee in that the recommended new simulations would be an excellent inclusion in future papers.  Please see our modified conclusion, last paragraph.

@@

%%4
\par\noindent
\item
\textsf
{The effect of gravity is neglected which potentially obliterates the results. It is not at all clear that the effect of the shear flow can be separated from that of gravity without rendering the results meaningless for any practical application. Even when one wants to do so it needs to be considered that the bubbles will be deformed into an ellipsoidal shape. Then at least the influence of initial condition has to be checked in order to ensure that the results make any sense. \\}
\vspace{3 mm}

Response: \\
We disagree that not including gravity ``obliterates'' the results.

### 2024-11-29 Revised-paper/Reply/Reply-Reviewer2.tex

Please find enclosed the revised version of our manuscript (CES-D-24-01867):
``Numerical Simulation of Bubble Deformation and Breakup under 
Simple Linear Shear Flows''.
We thank the reviewers for their comments and thoughts regarding improvement 
of our paper. We believe that we have addressed all of the reviewers’ 
concerns; the changes are itemized in detail below.

\par\noindent
NOTE: all references to equations and figures below are with
reference to the numbering scheme of the revised version of the paper,
not the original version.  Also, changes are hi-lighted in red.
\par\noindent

Changes made in response to comments of Reviewer 2: \begin{enumerate}
%%1
\item
\textsf
{Why are there several words in italics in the Introduction section and some other parts?}
\vspace{3 mm}

Response: \\
The italic format was used to emphasize certain passages, but in retrospect, we agree that which passages deserve italics and which passages don't is open to discretion.  So we have removed all the italics. \\

@@

%%2
\item
\textsf
{Page 2 Line 14: There should be an "and" before "Renardy"}
\vspace{3 mm}

Response: \\
We have corrected this mistake.  Also we have made complete run-throughs of the  paper checking for grammar errors and awkward sentences. \\
\\

@@

%%3
\par\noindent
\item
\textsf
{The authors mentioned several DNS methods in the Introduction section while choosing the CLSVOF method in this work. What are the reasons?}
\vspace{3 mm}

Response: \\
We have improved the introduction and section 3.1 in order to make it more clear about our rationale for using the CLSVOF method to capture complex deforming boundaries and also why we represent the gas-liquid interface as ideally sharp.  Also, we have already applied the CLSVOF method in past work to many multiphase flow problems with complex interface deformations.  Please see the top of section 3.2 in which we list past research in which we have obtained nice results for hard multiphase flow problems using the CLSVOF method.  \\

@@

%%4
\par\noindent
\item
\textsf
{Why can the effect of gravity be disregarded in this work?\\}
\vspace{3 mm}

Response: \\
In our computations, we set $g = 0$ because we wanted to isolate only the effects of the density and viscosity ratios and 
wanted to compare with previous studies dealing with the deformation and breakup of a drop with $\lambda =1$ and $\eta = 1$. 
Also, in the revised paper, a brief discussion of the potential influence of gravity (Froude number) on bubble breakup dynamics 
has been added according to another reviewer's suggestion.\\ \\
Please see the remark in section 2.  \\

@@

%%6
\par\noindent
\item
\textsf
{Page 14: What are the units of the variable T?.}
\vspace{3 mm}

Response: \\
$T$ is the dimensionless time defined by $T$ =$\mathit{\Gamma} t$.  Please see
equation (8) in the revision. \\
\\

%%7
\par\noindent
\item
\textsf
{Figure 4: Drop deformation and breakup are compared under conditions with $Re$ = 1.0 and 1.1. When $Re$ = 1.0, the simulation ends at $T$ = 35.0, and it is stated that drops will not break up. When $R$ = 1.1, the drop also does not break up at $T$ = 35.0. It breaks up at $T$ = 56.7. What about also showing the status of drop under $Re$ = 1.0 at $T$ = 56.7? It might be a more reasonable comparison.}
\vspace{3 mm}

Response: \\
We agree with the reviewer's suggestion. We added results at $T$ = 40.1, 50.0, and 56.7 to the drop case for $Re$ = 1.0 in Fig. 4.  As can be seen from the new Fig. 4, a drop remains a stable deformed state after $T$ = 35.0. In the revised paper, such a comment was added.\\
\\

### 2024-11-29 Revised-paper/Reply/Reply-Reviewer3.tex

Please find enclosed the revised version of our manuscript (CES-D-24-01867):
``Numerical Simulation of Bubble Deformation and Breakup under 
Simple Linear Shear Flows''.
We thank the reviewers for their comments and thoughts regarding improvement 
of our paper. We believe that we have addressed all of the reviewers’ 
concerns; the changes are itemized in detail below.

\par\noindent
NOTE: all references to equations and figures below are with
reference to the numbering scheme of the revised version of the paper,
not the original version.  Also, changes are hi-lighted in red.
\par\noindent

Changes made in response to comments of Reviewer 3: \begin{enumerate}
%%1
\item
\textsf
{The manuscript needs extensive revision for language and grammar.}
\vspace{3 mm}

Response: \\
We carefully made multiple run-throughs of our paper fixing all English errors and awkward constructs.\\

@@

%%3
\par\noindent
\item
\textsf
{Improve your figures.}
\vspace{3 mm}

Response: \\
We are confused about the reviewer's comment because the reviewer did not provide which figures to improve.
We carefully checked all the figures and improved Figs. 4, 5, and 10.\\
\\

%%4
\par\noindent
\item
\textsf
{What is the novelty of your study?\\
Discuss about other studies on numerical simulation of bubble deformation. How your study differs?\\
Improve Introduction section.\\}
\vspace{3 mm}

Response: \\
We have completely rewritten the introduction in order to make our message very clear.
\par
To summarize: \\
We have referred to and explained previous studies about bubble deformation and breakup in the ``Introduction.''
Besides, we have stated the novelty of this study and the difference between this study and previous studies.
In previous experimental studies on the motion of bubble deformation in a simple shear flow, only bubble deformation under very 
low $Re$ number conditions ($Re \ll 1$) have been examined.  
Meanwhile, only a few studies have been reported for the numerical simulation of bubble deformation and breakup in a simple shear flow.
These previous studies mainly examined the dynamics of bubble deformation in a shear flow.
Concerning bubble breakup, Wei et al. (2012) presented only one numerical result for a bubble breakup process under 
the condition of $Ca$ (capillary number) = 35.  
In this study, we first determined the critical Reynolds number ($Re \gg 1$) that leads to bubble breakup for $Ca = 0.3 \sim 1.0$.
This is the largest novelty in this study.
Additionally, our study revealed characteristics that distinguish a drop's deformation and breakup processes from a bubble.\\
In the revised paper, we have completely modified the ``Introduction".  \\
\\
Again, please see the revised ``Introduction.''  The Introduction is better now.
\\

@@

%%4
\par\noindent
\item
\textsf
{The conclusions are not supported by the results and discussion.}
\vspace{3 mm}

Response: \\
We carefully checked the ``Conclusions,'' and believe the results and discussion properly support our conclusions.\\
We have made some minor alterations to the ``Conclusions.'' Also, we have added an additional paragraph which gives suggestions for future research. \\
\\
Please see the improved ``Conclusions.'' 
\\

### 2024-11-29 Revised-paper/Reply/Reply-Reviewer4.tex

Please find enclosed the revised version of our manuscript (CES-D-24-01867):
``Numerical Simulation of Bubble Deformation and Breakup under 
Simple Linear Shear Flows''.
We thank the reviewers for their comments and thoughts regarding improvement 
of our paper. We believe that we have addressed all of the reviewers’ 
concerns; the changes are itemized in detail below.

\par\noindent
NOTE: all references to equations and figures below are with
reference to the numbering scheme of the revised version of the paper,
not the original version.  Also, changes are hi-lighted in red.
\par\noindent

Changes made in response to comments of Reviewer 4: 
\begin{enumerate}
%%1
\item
\textsf
{The investigated ranges of density ratio ($\lambda$) and viscosity ratio ($\eta$) could be expanded to encompass lower values, which 
would be applicable to various gas-liquid systems, including molten metal processes and slurry bubble columns.}
\vspace{3 mm}

Response: \\
Thank you for your kind comments.  In the revised paper, we have completely modified the ``Introduction'' and improved the motivation for our research.\\
\\

@@

%%2
\par\noindent
\item
\textsf
{Additional details regarding the computational tools/code and algorithms employed would enhance the reproducibility of the 
results presented in this study.}
\vspace{3 mm}

Response: \\
Thank you very much for your suggestions.  Please see the top of section 3.2 which now references our past work on the algorithm that is employed in this paper.
\\

@@

%%3
\par\noindent
\item
\textsf
{The authors should elucidate the rationale behind constraining the viscosity ratio to values below $10^{-3}$.}
\vspace{3 mm}

Response: \\
In the paper, we already described physical properties (density, viscosity, surface tension) set in the computations:\\
\\
Bubble: $\rho_{\rm b}$ = 1.2 kg/m$^{3}$ and $\mu_{\rm b} = 1.8 \times 10^{-5} $ Pa$\cdot$s\\
Liquid:  $\rho_{\rm m}$ = 1000 kg/m$^{3}$ and $\mu_{\rm m}$ = a changeable value corresponding to $Ca$ [Pa$\cdot$s]\\
Surface tension : $\sigma =2.5 \times 10^{-2}$ N/m. \\
Then, $\mu_{\rm m}$ had $2.0 \times 10^{-2} \sim 6.0 \times 10^{-2}$ Pa$\cdot$s and
$V$ had about 1.1 $\sim$ 1.3 m/s for the range of $Ca$ and $Re$ in our computaions.\\
When $\mu_{\rm m}$ = $2.0 \times 10^{-2} \sim 6.0 \times 10^{-2}$ Pa$\cdot$s, we have $\eta < 1.0 \times 10^{-3}$.\\
We have added the range of $\mu_{\rm m}$ and $V$ used in this study.\\
\\

%%4
\par\noindent
\item
\textsf
{While gravitational effects were not considered in this investigation, a brief discussion of the potential influence 
of the Froude number (Fr) on bubble breakup dynamics would provide valuable context.}
\vspace{3 mm}

Response: \\
We agree with the reviewer's comment.  \\
In our computations, we set $g = 0$ because we wanted to isolate only the effects of the density and viscosity ratios and 
wanted to compare previous studies dealing with the deformation and breakup of a drop with $\lambda =1$ and $\eta = 1$.
When the gravity is considered, we obtain $Fr$ (Froude number) $\left(= \frac{{\it \Gamma}R}{\sqrt {gR}} \right)$ = 1.7 ($Re$ = 93 and $Ca$ = 0.3) 
and 1.9 ($Re = 43$ and $Ca$ = 0.8). \\
Although the values of $Fr$ are not so large, the effect of gravity (bubble rise motion) may not be completely negligible in terms of $Fr$.
However, bubbles for both conditions reach the breakup at $t$ = about 0.5 s. 
Accordingly, it is expected that the effect of gravity (bubble rise motion) can be negligible to the behavior of bubble deformation and breakup 
around critical $Re$ number conditions.
In the revised paper, we have described these explanations.\\
\\
Please see line 181 in section 2 (the definiton of $Fr$) and the remark in section 2.
\\

### 2024-11-29 Revised-paper/Paper/Bubble-deformation-Rev.tex
hand off back to Mitsuhiro

%\usepackage[dvipdfmx]{graphicx}% Include figure files
%\usepackage{graphicx}% Include figure files
%\usepackage{caption}
%\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{comment}
\usepackage{color}
\usepackage{comment}
% line numbers
\usepackage{lineno}
%\usepackage{ragged2e}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\author[1,2]{Mitsuhiro Ohta\corref{cor1}} 
\cortext[cor1]{Corresponding author: m-ohta@tokushima-u.ac.jp}
\begin{comment} 
\affiliation[1]{
  organization={Department of Mechanical Science, Graduate School of Technology, 
                Industrial and Social Sciences, Tokushima University},
  addressline={2-1 Minamijyousanjima-cho},
  state={Tokushima 770-8506}, 
  country={Japan}}
\affiliation[2]{
  organization={Department of Mechanical Engineering, Graduate School of Technology, 
                Industrial and Social Sciences, Tokushima University},
  addressline={2-1 Minamijyousanjima-cho},
  state={Tokushima 770-8506}, 
  country={Japan}}
\end{comment}

@@

\begin{comment} 
\affiliation[3]{
  organization={High Performance Plastics Company, Sekisui Chemical Co., Ltd.},
  addressline={2-1 Hyakuyama, Mishimagun Shimamoto-cho},
  state={Osaka 618-0021}, 
  country={Japan}}
\end{comment}

@@

\author[4]{Edwin Jimenez}  
\begin{comment} 
\affiliation[4]{
  organization={Spectral Numerical, LLC},
  addressline={1942 Broadway St., STE 314C},
  city={Boulder},
  state={CO 80302},
  country={USA}}
\end{comment}

\author[5]{Mark Sussman}  
\begin{comment} 
\affiliation[5]{
  organization={Department of Mathematics, Florida State University},
  city={Tallahassee},
  state={FL 32306},
  country={USA}}
\end{comment}

@@

Bubble dynamics in shear flow, including breakup, is critically important for various \textcolor{blue} {gas-liquid} scientific and engineering processes.  We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, underwater projectiles, polyethylene devolatilization, microfluidics, food aeration, passive cyclonic separators, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble,CanedoETAL,GAO2022103212,WONG2012417,PolyethyleneDevo,FRENSE2024120579,lohse2018bubble,schluter2021small,SANOGO2023112478,hoyt2013performance,sines2020study}.  In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.

@@

\textcolor{blue} 

@@

The numerical results presented in this and the previous section used a finest-level grid size set to $\Delta x^{\ell=1}(= \Delta y^{\ell=1}= \Delta z^{\ell=1})=R/16$. To verify the adequacy of this grid resolution, we present rid refinement results for a bubble breakup simulation with $Ca=1.0$, which corresponds to the most deformable and stretchable bubble case considered in our numerical studies. We use three different grid systems, (i) $\Delta x^{\ell=1}=R/8$, (ii) $\Delta x^{\ell=1}=R/16$, and (iii) $\Delta x^{\ell=1}=R/24$, in order to determine $Re_{\rm c}$.  Figure~\ref{fig:DeEvolution} shows the time evolution of the deformation parameter $D$ over time for the three grid systems; the $x$-axis is a dimensionless time defined by $T=\mathit{\Gamma} t$ and the $y$-axis is $D$.  The results show that bubble breakup occurs at $Re_{\rm c}$ = 35 for the grid system with $\Delta x^{\ell=1}=R/16$, while the finer computational grid with $\Delta x^{\ell=1}=R/24$ predicts a critical value of $Re_{\rm c}$ = 34.  For the $\Delta x^{\ell=1}=R/8$ results, it is clear that the $R/8$ resolution is too coarse to capture the proper break-up time, albeit the critical Reynolds' number, $Re_{\rm c}$ = 33, was still close to the finer grid resolution cases.  Note that although the time evolution of $D$ for the two finer resolution systems ($R/16$ and $R/24$) is consistent between the two (the predicted critical Reynolds numbers differ by $\sim 3\%$), the computational time using the grid system with $\Delta x^{\ell=1}=R/24$ was more than 6 times longer than the one based on the coarser system with $\Delta x^{\ell=1}=R/16$.  We remark that in our search for $Re_{\rm c}$, we considered a wide range of values of $Ca$, and we found it necessary to use a large $L$ ($\sim 24R$) since for certain shear flows the bubble can stretch significantly without breaking up.  Nevertheless, for the conditions presented in this section, the results indicate that our numerical approach, even with a finest-level resolution set to $\Delta x^{\ell=1}=R/16$, is capable of accurately reproducing bubble deformation and breakup without sacrificing any essential dynamical features.

@@

\subsection{Drop deformation and breakup}\label{sec:DropBreak}
%  -----------------------------------------------------------------------------
% 
%\begin{comment} 
\begin{figure}%[h!]
  \centering
  \textcolor{red}
{
  \includegraphics[width=\textwidth]{Figure/4-DropBreakEvol}
  \caption{Time evolution of drop deformation and breakup in shear flow at the
           condition of $Ca=0.3$ with (a) $Re=1.0$ and (b) $Re=1.1$.  The
	   ``drop'' critical Reynolds number corresponding to $Ca=0.3$ is
	   $1.0<Re_{\rm c}<1.1$.
	   ($\lambda$ = $\eta$ = 1.0)}
 }
  \label{fig:DropBreak}
\end{figure}
%\end{comment} 
%
To illustrate the differences in deformation and breakup between a drop and a bubble around critical conditions, we first present numerical results for drop deformation.  The time evolution of drop deformation and breakup in simple linear shear flow for two conditions is shown in Figure \ref{fig:DropBreak}; the first case, shown in Figure ~\ref{fig:DropBreak}(a), uses $Ca=0.3$ and $Re=1.0$, while the second case, depicted in Figure ~\ref{fig:DropBreak}(b), uses $Ca=0.3$ and $Re=1.1$.  Using a domain size of $\lwh{24}{6}{6}$, in the case with $Re=1.0$, the drop gradually deforms and finally attains a stable deformed state.

>>>>

%\usepackage[dvipdfmx]{graphicx}% Include figure files
%\usepackage{graphicx}% Include figure files
%\usepackage{caption}
%\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{comment}
% line numbers
\usepackage{lineno}
%\usepackage{ragged2e}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\author[1,2]{Mitsuhiro Ohta\corref{cor1}} 
\cortext[cor1]{Corresponding author: m-ohta@tokushima-u.ac.jp}
%\begin{comment} 
\affiliation[1]{
  organization={Department of Mechanical Science, Graduate School of Technology, 
                Industrial and Social Sciences, Tokushima University},
  addressline={2-1 Minamijyousanjima-cho},
  state={Tokushima 770-8506}, 
  country={Japan}}
\affiliation[2]{
  organization={Department of Mechanical Engineering, Graduate School of Technology, 
                Industrial and Social Sciences, Tokushima University},
  addressline={2-1 Minamijyousanjima-cho},
  state={Tokushima 770-8506}, 
  country={Japan}}
%\end{comment}

@@

%\begin{comment} 
\affiliation[3]{
  organization={High Performance Plastics Company, Sekisui Chemical Co., Ltd.},
  addressline={2-1 Hyakuyama, Mishimagun Shimamoto-cho},
  state={Osaka 618-0021}, 
  country={Japan}}
%\end{comment}

@@

\author[4]{Edwin Jimenez}  
%\begin{comment} 
\affiliation[4]{
  organization={Spectral Numerical, LLC},
  addressline={1942 Broadway St., STE 314C},
  city={Boulder},
  state={CO 80302},
  country={USA}}
%\end{comment}

\author[5]{Mark Sussman}  
%\begin{comment} 
\affiliation[5]{
  organization={Department of Mathematics, Florida State University},
  city={Tallahassee},
  state={FL 32306},
  country={USA}}
%\end{comment}

@@

Bubble dynamics in shear flow, including breakup, is critically important for various gas-liquid scientific and engineering processes.  We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, underwater projectiles, polyethylene devolatilization, microfluidics, food aeration, passive cyclonic separators, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble,CanedoETAL,GAO2022103212,WONG2012417,PolyethyleneDevo,FRENSE2024120579,lohse2018bubble,schluter2021small,SANOGO2023112478,hoyt2013performance,sines2020study}.  In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.

@@

@@

The numerical results presented in this and the previous section used a finest-level grid size set to $\Delta x^{\ell=1}(= \Delta y^{\ell=1}= \Delta z^{\ell=1})=R/16$. To verify the adequacy of this grid resolution, we present rid refinement results for a bubble breakup simulation with $Ca=1.0$, which corresponds to the most deformable and stretchable bubble case considered in our numerical studies. We use three different grid systems, (i) $\Delta x^{\ell=1}=R/8$, (ii) $\Delta x^{\ell=1}=R/16$, and (iii) $\Delta x^{\ell=1}=R/24$, in order to determine $Re_{\rm c}$.  Figure~\ref{fig:DeEvolution} shows the time evolution of the deformation parameter $D$ over time for the three grid systems; the $x$-axis is a dimensionless time defined by,
\textcolor{red}{
\begin{eqnarray}
T=\Gamma t,
\end{eqnarray}
}
and the $y$-axis is $D$.  The results show that bubble breakup occurs at $Re_{\rm c}$ = 35 for the grid system with $\Delta x^{\ell=1}=R/16$, while the finer computational grid with $\Delta x^{\ell=1}=R/24$ predicts a critical value of $Re_{\rm c}$ = 34.  For the $\Delta x^{\ell=1}=R/8$ results, it is clear that the $R/8$ resolution is too coarse to capture the proper break-up time, albeit the critical Reynolds' number, $Re_{\rm c}$ = 33, was still close to the finer grid resolution cases.  Note that although the time evolution of $D$ for the two finer resolution systems ($R/16$ and $R/24$) is consistent between the two (the predicted critical Reynolds numbers differ by $\sim 3\%$), the computational time using the grid system with $\Delta x^{\ell=1}=R/24$ was more than 6 times longer than the one based on the coarser system with $\Delta x^{\ell=1}=R/16$.  We remark that in our search for $Re_{\rm c}$, we considered a wide range of values of $Ca$, and we found it necessary to use a large $L$ ($\sim 24R$) since for certain shear flows the bubble can stretch significantly without breaking up.  Nevertheless, for the conditions presented in this section, the results indicate that our numerical approach, even with a finest-level resolution set to $\Delta x^{\ell=1}=R/16$, is capable of accurately reproducing bubble deformation and breakup without sacrificing any essential dynamical features.

@@

\subsection{Drop deformation and breakup}\label{sec:DropBreak}
%  -----------------------------------------------------------------------------
% 
%\begin{comment} 
\begin{figure}%[h!]
  \centering
  \textcolor{red}
{
  \includegraphics[width=\textwidth]{Figure/4-DropBreakEvol}
  \caption{Time evolution of drop deformation and breakup in shear flow at the
           condition of $Ca=0.3$ with (a) $Re=1.0$ and (b) $Re=1.1$.  The
	   ``drop'' critical Reynolds number corresponding to $Ca=0.3$ is
	   $1.0<Re_{\rm c}<1.1$.
	   ($\lambda$ = $\eta$ = 1.0) \label{fig:DropBreak} }
 }

\end{figure}
%\end{comment} 
%
To illustrate the differences in deformation and breakup between a drop and a bubble around critical conditions, we first present numerical results for drop deformation.  The time evolution of drop deformation and breakup in simple linear shear flow for two conditions is shown in Figure \ref{fig:DropBreak}; the first case, shown in Figure ~\ref{fig:DropBreak}(a), uses $Ca=0.3$ and $Re=1.0$, while the second case, depicted in Figure ~\ref{fig:DropBreak}(b), uses $Ca=0.3$ and $Re=1.1$.  Using a domain size of $\lwh{24}{6}{6}$, in the case with $Re=1.0$, the drop gradually deforms and finally attains a stable deformed state.
